Teaching a Class to Grade Itself using Game Theory

### 2013-09-14 Primes Write up.tex
Finished up methods and materials

\section{Materials and Methods}
To create the models that are used to predict the behavior of the students, a set process was used each time. To begin with, a set of assumptions is created. These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades. This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model. The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side. To begin with, a simple set of assumptions was created:
%Note: Specify that the model refers to a single grading round: There are $n$ students and 1 professor. Every student comes to us with an ungraded paper (input) define the objective score o_i, we then give those papers grades(output) After a mechanism runs each student receives a grade $g_i$ and after performing $w_i$ units of work. Define the professor as index 0.%
\begin{enumerate}
  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
  \item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
  \item Students want to maximize their final happiness, expressed as $H(g)-W$
  \item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting x and y each with 50 percent chance, gives a happiness of 7.5).
  \item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It doesn't depend on the score of others
\end{enumerate}
%add simple list%

%Explanation of the choice of assumption
% - We need to talk about happiness because it provides a numerical way to compare different outcomes
% - Why don't we care about our friends

%First objective%
No student can deviate from the truthful strategy to improve his happiness. In math terms, if by acting honestly student i grades $w_i$ papers and gets a grade of $g_i$ there shouldn't be any way for the student to spend $w'_i$ units of effort and get a score $g'_i$ where $H(g'_i)-w'_i > H(g_i)-w_i$.

@@

Once a simple set of assumptions and a benchmark were created, the assumptions need to be further developed into a true model that will become the ``''rules'' of the game. To do this, a model was created that will simulate the environment of a classroom, based on the observations of students inside real classes. This turned the list of assumptions from the 
simple into:
%Repeat above corrections%
\begin{enumerate}
\item The objective score of an assignment is from 0 to 100%setting%
\item The objective score assigned by the professor is the correct objective score%setting%
\item Grading is binary, a grader can either grade or not grade, \emph{i.e} there is no way to use 0.5 units of effort

\item Not everyone has the ability to get the correct objective score

\item Every assignment costs 1 unit of effort, no matter who grades or how difficult the assignment
\item Students want good grades
\item People don't like doing work
\item Students are selfish and don't care about their friends
\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
\item Everyone is risk neutral with respect to happiness

\item All students can communicate with all other students

\end{enumerate}

Put simply, in a given class of \emph{n} students and 1 professor, students must submit assignments, each of which have grades on a scale of 0 to 100. All of these assignments must be graded by someone, and no one can grade their own assignment. Grading one of the assignments costs 1 unit of effort, and will always find the correct score, \emph{i.e} the \emph{objective score}, and grading is the only way to find this objective score.

@@

\section{The Problem}
In a given class of \emph{n} students and 1 professor, students must submit assignments, each of which have grades on a scale of 1 to 100. All of these assignments must be graded by someone, and no one can grade their own assignment. Our goal is to come up with a scheme that minimizes the maximum amount of work done by a single person, as well as the maximum deviation between any student's given grade and the grade their assignment deserves.

>>>>

\section{Materials and Methods}
\subsection{The Scenario}
In our trying to find a solution to the professor's problem, we created a scenario in which our solution applies to a single assignment. This means that our system will have to be repeated for every assignment, instead of performing on a global scale. In such a "round" of grading, there are $n$ students, who each bring one ungraded paper to the professor. These ungraded papers are like the input for a function. Each of these papers has an objective score $o_i\mid 0<o_i<100$. This is the score the professor would give out. Our mechanism then grades the paper, and outputs these grades. After one "round" each student receives a grade $g_i$ and after performing $w_i$ units of work, where for one paper, $w_i=1$. The professor is index 0.
\subsection{Assumptions}
To create the models that are used to predict the behavior of the students, a set process was used each time. To begin with, a set of assumptions is created. These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades. This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model. The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side. To begin with, a simple set of assumptions was created:
\begin{enumerate}
	\item Students want good grades
 	\item Doing work makes students unhappy
  	\item Students want to be happy
 	\item Students only care about their final happiness
  	\item The happiness of a student is only affected by their grade and the amount of work they do
\end{enumerate}
However, we wanted to create a mathematical solution, so these assumptions need to be changed into math terms. The result of this is as follows:
\begin{enumerate}
  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
  \item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
  \item Students want to maximize their final happiness, expressed as $H(g)-W$
  \item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting x and y each with 50 percent chance, gives a happiness of 7.5).
  \item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It doesn't depend on the score of others
\end{enumerate}

\subsection{Why?}
There are two questions that need to be addressed, first, why is happiness important, and second, why are the scores of others not important? The importance of happiness lies in the fact that it provides a way to compare different outcomes; effectively allowing us to show definitively which of two models is better. The reasoning for not caring about friends is due to the relatively low impact they have on someone's grades and happiness, as well as the incredible complexity the model would have to account for with this considered.
\subsection{First major objective}
No student can deviate from the truthful strategy to improve his happiness. In math terms, if by acting honestly student i grades $w_i$ papers and gets a grade of $g_i$ there shouldn't be any way for the student to spend $w'_i$ units of effort and get a score $g'_i$ where $H(g'_i)-w'_i > H(g_i)-w_i$.

@@

Once a simple set of assumptions and a benchmark were created, the assumptions need to be further developed into a true model that will become the ``''rules'' of the game. To do this, a model was created that will simulate the environment of a classroom, based on the observations of students inside real classes. This turned the list of assumptions from the 
simple into:
%Repeat above corrections%
\begin{enumerate}
\item When grading, $w_i=0 \oplus w_i=1$
\item For all students, $g_i \neq o_i$
\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral.
\item For a given student in $N$, that student has contact with all other students in $N$.
\end{enumerate}
Put simply:
\begin{enumerate}
\item Students cannot "half bake" an assignment
\item Students can't always get the exact objective score
\item Students want good grades
\item Students don't like grading
\item Students are selfish
\item Doing work costs 1 unit of effort
\item Students are risk neutral with respect to happiness
\item All students can talk to each other
\end{enumerate}

@@

\section{Results}
In a given class of \emph{n} students and 1 professor, students must submit assignments, each of which have grades on a scale of 1 to 100. All of these assignments must be graded by someone, and no one can grade their own assignment. Our goal is to come up with a scheme that minimizes the maximum amount of work done by a single person, as well as the maximum deviation between any student's given grade and the grade their assignment deserves.
